### 2014-02-25 paper/retrofit.tex
Fix erase, and proof.

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified. The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will get filtered
    by |erasef il| in |ic1'|.
    Finally, lets consider the possible changes to |iS1|: If |it1| sends a
    message, then the corresponding queue in |iS1'| will contain one
    more message.  However, that message has the label of |it1| (or a higher
    label), and will thus get erased by |erasef il|.
    \Red{The task could also send a message}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.

@@

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
    get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il| equivalent).
    \Red{Actually show this}
  \end{itemize}
\end{proof}

>>>>

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il nil = nil|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified. The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will get filtered
    by |erasef il| in |ic1'|.
    Lets consider the possible changes to |iS1|: If |it1| sends a
    message, then the corresponding queue in |iS1'| will contain one
    more message.  However, that message has the label of |it1| (or a higher
    label), and will thus get erased by |erasef il|.
    Finally, receiving or not receiving a message (by
    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
    task |it1|, which are erased from |iS1|.
    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.

@@

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first task |it1| and |it2| don't
    get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il| equivalent).
    Again, only send and receive will change |iS|, so we consider all
    rules that could have been used for~\eqref{eq:tsni-lemma-rhs}.  If
    a message is sent, then the message is added to the same queue.  This
    queue is either completely erased, or it is |il| equivalent.  In both
    cases, |il| equivalence of |iS1'| and |iS2'| is preserved.
    When the tasks are receiving a message, then by the reduction rules
    we know that they first filter the queue by the label of |it1|.  We
    also know that the queues are equivalent when filtered by the less
    restrictive label |il|, thus the messages received (or dropped) from the
    queue are equivalent.
  \end{itemize}
\end{proof}
